Paper_analysisandtables

### 2024-11-15 Code/Paper_analysisandtables.Rmd
Catch up

```{r setup, include=FALSE, echo=FALSE}
#MARKDOWN SETTINGS
knitr::opts_knit$set(root.dir = "/Users/KristinDobbin/Box Sync/Projects/R_Projects/Votingrights_systemperformance", warning=FALSE, message=FALSE, include=FALSE)

@@

compositemodellist <- list(WQ1, WQ1OR, Affordability1, Affordability1OR,
                           Accessibility1, Accessibility1OR, TMF1, TMF1OR)

Compositestable <- capture.output(stargazer(compositemodellist,
                                 type = 'html', 
                                 column.labels = c("coefficients(se)", "Odds ratio", 
                                                   "coefficients(se)", "Odds ratio", 
                                                   "coefficients(se)", "Odds ratio", 
                                                   "coefficients(se)", "Odds ratio"),
                                 model.numbers = FALSE, 
                                 dep.var.labels = c("Water quality", "Affordability", 
                                                    "Accessibility", "TMF"), 
                                 ci=c(F,T, F, T, F, T, F, T), 
                                 star.cutoffs = c(0.05, 0.01, 0.001),
                                 p = c(p.valuesWQ1, p.values2, pvaluesAffordability1, p.values2,
                                       pvaluesAccesibility1, p.values2, pvaluesTMF1, p.values2),
                                 omit.stat = c("ll", "aic"),
                                 covariate.labels = c("Lim enfran.", "No enfran.",
                                                      "Population (log)", "Surface water",
                                                      "Purchased"),
                                 omit = "Constant",
                                apply.ci = function(x) { 0 }))

@@

>>>>

```{r setup, include=FALSE, echo=FALSE}
#MARKDOWN SETTINGS
#knitr::opts_knit$set(root.dir = "/Users/KristinDobbin/Documents/Projects/R_Projects/Votingrights_systemperformance", warning=FALSE, message=FALSE, include=FALSE)

@@

compositemodellist <- list(WQ1, WQ1OR, Affordability1, Affordability1OR,
                          TMF1, TMF1OR)

Compositestable <- capture.output(stargazer(compositemodellist,
                                 type = 'html', 
                                 column.labels = c("coefficients(se)", "Odds ratio", 
                                                   "coefficients(se)", "Odds ratio", 
                                                   "coefficients(se)", "Odds ratio"),
                                 model.numbers = FALSE, 
                                 dep.var.labels = c("Water quality", "Affordability", 
                                                    "TMF"), 
                                 ci=c(F,T, F, T, F, T), 
                                 star.cutoffs = c(0.05, 0.01, 0.001),
                                 p = c(p.valuesWQ1, p.values2, pvaluesAffordability1, p.values2,
                                       pvaluesTMF1, p.values2),
                                 omit.stat = c("ll", "aic"),
                                 covariate.labels = c("Lim enfran.", "No enfran.",
                                                      "Population (log)", "Surface water",
                                                      "Purchased"),
                                 omit = "Constant",
                                apply.ci = function(x) { 0 }))

@@

```{r descriptives for demofraphics, results='asis', echo=FALSE}
Data_mini <- Data %>% select(enfranchisement_final, MHI, MHI_KD, LN_POP, Source, Percent.renter, Percent.white, POPULATION, CALENVIRO_SCREEN_SCORE, FAILING, WQ_combined_any, Affordability_combined_any, TMF_combined_any, Accessibility_combined_any, Percent.hispanicorlatino, Percent.black, Percent.asian)

Descriptives<- Data_mini %>%
  group_by(enfranchisement_final) %>% 
  summarize(meanLNPOP = mean(na.omit(POPULATION)),
            meanMHI = mean(na.omit(MHI)),
            meanPercRent = mean(na.omit(Percent.renter)),
            meanPercWhite = mean(na.omit(Percent.white)),
            meanCES = mean(na.omit(CALENVIRO_SCREEN_SCORE)),
            medianpop = median(na.omit(POPULATION)))

SIdescriptives <- Data_mini %>% 
  group_by(enfranchisement_final) %>% 
  select_if(is.numeric) %>% 
  gather(Variable, Value, -enfranchisement_final) %>% 
  group_by(Variable, enfranchisement_final) %>% 
  summarise(min = min(na.omit(Value)), 
            median = median(na.omit(Value)),
            mean = mean(na.omit(Value)), 
            max = max(na.omit(Value)),
            sd = sd(na.omit(Value))) %>% 
 ungroup()

SIdescriptives <- SIdescriptives %>% mutate_if(is.numeric, round, digits=3)
```
